### 2023-03-21 final_files/main.tex
formatting

\usepackage{natbib}
\bibliographystyle{unsrt}
\date{\today}

@@

JSW acknowledges support from the Chaire Blaise Pascal Program of the Île-de-France region.
The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.

@@

@@

\bibliography{main}

>>>>

\usepackage{natbib}
\bibliographystyle{pnas}
\date{\today}

@@

JSW acknowledges support from the Chaire Blaise Pascal Program of the Île-de-France region.
The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript. 
This manuscript was posted on a preprint: \url{https://www.medrxiv.org/content/10.1101/2022.08.01.22278288v1.full.pdf}.

@@

\section*{Author contribution}

SWP, JD, and JSW designed the project with input from BTG.
SWP and JSW performed model analysis.
SWP, JD,  and JSW analyzed model results.
SWP performed data analysis with input from all authors.
SWP, JD, BTG, and JSW wrote the paper.

@@

\begin{thebibliography}{10}

\bibitem{nogrady2020data}
B Nogrady, What the data say about asymptomatic {COVID} infections.
\newblock {\em {Nature}} \textbf{587}, 534--536 (2020).

\bibitem{rajgor2020many}
DD Rajgor, MH Lee, S Archuleta, N Bagdasarian, SC Quek, {The many estimates of
  the COVID-19 case fatality rate}.
\newblock {\em {The Lancet Infectious Diseases}}
  \textbf{20}, 776--777 (2020).

\bibitem{VERITY2020669}
R Verity, et~al., Estimates of the severity of coronavirus disease 2019: a
  model-based analysis.
\newblock {\em {The Lancet Infectious Diseases}}
  \textbf{20}, 669--677 (2020).

\bibitem{yang2020early}
S Yang, et~al., {Early estimation of the case fatality rate of COVID-19 in
  mainland China: a data-driven analysis}.
\newblock {\em {Annals of translational medicine}}
  \textbf{8} (2020).

\bibitem{levin2020assessing}
AT Levin, et~al., {Assessing the age specificity of infection fatality rates
  for COVID-19: systematic review, meta-analysis, and public policy
  implications}.
\newblock {\em {European journal of epidemiology}}
  \textbf{35}, 1123--1138 (2020).

\bibitem{emery2020}
JC Emery, et~al., {The contribution of asymptomatic SARS-CoV-2 infections to
  transmission on the Diamond Princess cruise ship}.
\newblock {\em {eLife}} \textbf{9}, e58699 (2020).

\bibitem{ggplot2}
H Wickham, {\em {ggplot2: Elegant Graphics for Data Analysis}}.
\newblock (Springer-Verlag New York), (2016).

\bibitem{Kissler2020}
SM Kissler, et~al., {Viral dynamics of acute SARS-CoV-2 infection}.
\newblock {\em {medRxiv}} (2021).

\bibitem{davies2020}
NG Davies, et~al., {Age-dependent effects in the transmission and control of
  COVID-19 epidemics}.
\newblock {\em {Nature Medicine}} \textbf{26}, 1205--1211
  (2020).

\bibitem{gao2021role}
W Gao, J Lv, Y Pang, LM Li, {Role of asymptomatic and pre-symptomatic
  infections in COVID-19 pandemic}.
\newblock {\em {bmj}} \textbf{375} (2021).

\bibitem{johansson2021sars}
MA Johansson, et~al., {SARS-CoV-2 transmission from people without COVID-19
  symptoms}.
\newblock {\em {JAMA network open}} \textbf{4},
  e2035057--e2035057 (2021).

\bibitem{subramanian2021quantifying}
R Subramanian, Q He, M Pascual, {Quantifying asymptomatic infection and
  transmission of COVID-19 in New York City using observed cases, serology, and
  testing capacity}.
\newblock {\em {Proceedings of the National Academy of
  Sciences}} \textbf{118}, e2019716118 (2021).

\bibitem{koelle2022changing}
K Koelle, MA Martin, R Antia, B Lopman, NE Dean, {The changing epidemiology of
  SARS-CoV-2}.
\newblock {\em {Science}} \textbf{375}, 1116--1121 (2022).

\bibitem{lizewski2022navy}
RA Lizewski, et~al., {SARS-CoV-2} outbreak dynamics in an isolated {US}
  military recruit training center with rigorous prevention measures.
\newblock {\em {Epidemiology}} \textbf{33} (2022).

\bibitem{mizumoto2020estimating}
K Mizumoto, K Kagaya, A Zarebski, G Chowell, {Estimating the asymptomatic
  proportion of coronavirus disease 2019 (COVID-19) cases on board the Diamond
  Princess cruise ship, Yokohama, Japan, 2020}.
\newblock {\em {Eurosurveillance}} \textbf{25}, 2000180
  (2020).

\bibitem{ferretti2020quantifying}
L Ferretti, et~al., {Quantifying SARS-CoV-2 transmission suggests epidemic
  control with digital contact tracing}.
\newblock {\em {Science}} \textbf{368}, eabb6936 (2020).

\bibitem{lavezzo2020}
E Lavezzo, et~al., {Suppression of a SARS-CoV-2 outbreak in the Italian
  municipality of Vo'}.
\newblock {\em {Nature}} \textbf{584}, 425--429 (2020).

\bibitem{romero2021ct}
MP Romero-G{\'o}mez, et~al., Ct value is not enough to discriminate patients
  harbouring infective virus.
\newblock {\em {Journal of Infection}} \textbf{82},
  e35--e37 (2021).

\bibitem{stadnytskyi2021breathing}
V Stadnytskyi, P Anfinrud, A Bax, {Breathing, speaking, coughing or sneezing:
  What drives transmission of SARS-CoV-2?}
\newblock {\em {Journal of Internal Medicine}}
  \textbf{290}, 1010--1027 (2021).

\bibitem{alene2021magnitude}
M Alene, et~al., {Magnitude of asymptomatic COVID-19 cases throughout the
  course of infection: A systematic review and meta-analysis}.
\newblock {\em {PloS one}} \textbf{16}, e0249090 (2021).

\bibitem{fraser2004factors}
C Fraser, S Riley, RM Anderson, NM Ferguson, Factors that make an infectious
  disease outbreak controllable.
\newblock {\em {Proceedings of the National Academy of
  Sciences}} \textbf{101}, 6146--6151 (2004).

\bibitem{moghadas2020implications}
SM Moghadas, et~al., {The implications of silent transmission for the control
  of COVID-19 outbreaks}.
\newblock {\em {Proceedings of the National Academy of
  Sciences}} \textbf{117}, 17513--17515 (2020).

\bibitem{xie2022long}
Y Xie, E Xu, B Bowe, Z Al-Aly, {Long-term cardiovascular outcomes of COVID-19}.
\newblock {\em {Nature medicine}} \textbf{28}, 583--590
  (2022).

\bibitem{he2020temporal}
X He, et~al., {Temporal dynamics in viral shedding and transmissibility of
  COVID-19}.
\newblock {\em {Nature Medicine}} \textbf{26}, 672--675
  (2020).

\bibitem{sender2021unmitigated}
R Sender, et~al., {The unmitigated profile of COVID-19 infectiousness}.
\newblock {\em {medRxiv}} (2021).

\bibitem{kucharski2020effectiveness}
AJ Kucharski, et~al., Effectiveness of isolation, testing, contact tracing, and
  physical distancing on reducing transmission of sars-cov-2 in different
  settings: a mathematical modelling study.
\newblock {\em {The Lancet Infectious Diseases}}
  \textbf{20}, 1151--1160 (2020).

\bibitem{lipsitch2020understanding}
M Lipsitch, NE Dean, Understanding {COVID-19} vaccine efficacy.
\newblock {\em {Science}} \textbf{370}, 763--765 (2020).

\bibitem{andres2022omicron}
N Andrews, et~al., Covid-19 vaccine effectiveness against the {Omicron
  (B.1.1.529)} variant.
\newblock {\em {New England Journal of Medicine}}
  \textbf{386}, 1532--1546 (2022).

\bibitem{pearson2021omicron}
CAB Pearson, et~al., {Bounding the levels of transmissibility \& immune evasion
  of the Omicron variant in South Africa}.
\newblock {\em {medRxiv}} (2021).

\bibitem{sun2022omicron}
K Sun, et~al., {Persistence of SARS-CoV-2 immunity, Omicron{\textquoteright}s
  footprints, and projections of epidemic resurgences in South African
  population cohorts}.
\newblock {\em {medRxiv}} (2022).

\bibitem{MENNI20221618}
C Menni, et~al., {Symptom prevalence, duration, and risk of hospital admission
  in individuals infected with SARS-CoV-2 during periods of omicron and delta
  variant dominance: a prospective observational study from the ZOE COVID
  Study}.
\newblock {\em {The Lancet}} \textbf{399}, 1618--1624
  (2022).

\bibitem{ulloa2022estimates}
AC Ulloa, SA Buchan, N Daneman, KA Brown, {Estimates of SARS-CoV-2 omicron
  variant severity in Ontario, Canada}.
\newblock {\em {Jama}} \textbf{327}, 1286--1288 (2022).

\bibitem{Iacobuccio254}
G Iacobucci, Covid-19: unravelling the conundrum of {Omicron} and deaths.
\newblock {\em {BMJ}} \textbf{376} (2022).

\bibitem{faust2022omicron}
JS Faust, et~al., {Excess Mortality in {Massachusetts} During the {Delta} and
  {Omicron} Waves of {COVID-19}}.
\newblock {\em {JAMA}} (2022).

\bibitem{sigal2022estimating}
A Sigal, R Milo, W Jassat, {Estimating disease severity of Omicron and Delta
  SARS-CoV-2 infections}.
\newblock {\em {Nature Reviews Immunology}} pp. 1--3
  (2022).

\bibitem{saad2020immune}
CM Saad-Roy, et~al., {Immune life history, vaccination, and the dynamics of
  SARS-CoV-2 over the next 5 years}.
\newblock {\em {Science}} \textbf{370}, 811--818 (2020).

\bibitem{gallagher2021indirect}
ME Gallagher, et~al., {Indirect benefits are a crucial consideration when
  evaluating SARS-CoV-2 vaccine candidates}.
\newblock {\em {Nature medicine}} \textbf{27}, 4--5 (2021).

\bibitem{park2020time}
SW Park, DM Cornforth, J Dushoff, JS Weitz, {The time scale of asymptomatic
  transmission affects estimates of epidemic potential in the COVID-19
  outbreak}.
\newblock {\em {Epidemics}} \textbf{31}, 100392 (2020).

\bibitem{harris2023time}
JD Harris, SW Park, J Dushoff, JS Weitz, How time-scale differences in
  asymptomatic and symptomatic transmission shape sars-cov-2 outbreak dynamics.
\newblock {\em {Epidemics}} p. 100664 (2023).

\bibitem{moore2021modelling}
S Moore, EM Hill, L Dyson, MJ Tildesley, MJ Keeling, {Modelling optimal
  vaccination strategy for SARS-CoV-2 in the UK}.
\newblock {\em {PLoS computational biology}} \textbf{17},
  e1008849 (2021).

\bibitem{weitz2020awareness}
JS Weitz, SW Park, C Eksin, J Dushoff, Awareness-driven behavior changes can
  shift the shape of epidemics away from peaks and toward plateaus, shoulders,
  and oscillations.
\newblock {\em {Proceedings of the National Academy of
  Sciences}} \textbf{117}, 32764--32771 (2020).

\bibitem{kissler2020projecting}
SM Kissler, C Tedijanto, E Goldstein, YH Grad, M Lipsitch, {Projecting the
  transmission dynamics of SARS-CoV-2 through the postpandemic period}.
\newblock {\em {Science}} \textbf{368}, 860--868 (2020).

\bibitem{lavine2021immunological}
JS Lavine, ON Bjornstad, R Antia, {Immunological characteristics govern the
  transition of COVID-19 to endemicity}.
\newblock {\em {Science}} \textbf{371}, 741--745 (2021).

\bibitem{gandon2001imperfect}
S Gandon, MJ Mackinnon, S Nee, AF Read, Imperfect vaccines and the evolution of
  pathogen virulence.
\newblock {\em {Nature}} \textbf{414}, 751--756 (2001).

\bibitem{Bavel2020}
JJV Bavel, et~al., {Using social and behavioural science to support COVID-19
  pandemic response}.
\newblock {\em {Nature Human Behaviour}} \textbf{4},
  460--471 (2020).

\bibitem{chande2020real}
A Chande, et~al., {Real-time, interactive website for US-county-level COVID-19
  event risk assessment}.
\newblock {\em {Nature Human Behaviour}} \textbf{4},
  1313--1319 (2020).

\bibitem{sinclair2021pairing}
AH Sinclair, S Hakimi, ML Stanley, RA Adcock, GR Samanez-Larkin, Pairing facts
  with imagined consequences improves pandemic-related risk perception.
\newblock {\em {Proceedings of the National Academy of
  Sciences}} \textbf{118}, e2100970118 (2021).

\bibitem{mina2021covid}
MJ Mina, KG Andersen, {COVID-19} testing: One size does not fit all.
\newblock {\em {Science}} \textbf{371}, 126--127 (2021).

\bibitem{gibson2022surv}
G Gibson, et~al., Surveillance-to-diagnostic testing program for asymptomatic
  {SARS-CoV-2} infections on a large, urban campus in fall 2020.
\newblock {\em {Epidemiology}} \textbf{33} (2022).

\bibitem{Ranoa2022}
DRE Ranoa, et~al., {Mitigation of SARS-CoV-2 transmission at a large public
  university}.
\newblock {\em {Nature Communications}} \textbf{13}, 3207
  (2022).

\bibitem{jones2020two}
NR Jones, et~al., Two metres or one: what is the evidence for physical
  distancing in {COVID-19?}
\newblock {\em {bmj}} \textbf{370} (2020).

\bibitem{prather2020reducing}
KA Prather, CC Wang, RT Schooley, Reducing transmission of {SARS-CoV-2}.
\newblock {\em {Science}} \textbf{368}, 1422--1424 (2020).

\bibitem{howard2021ev}
J Howard, et~al., {An evidence review of face masks against COVID-19}.
\newblock {\em {Proceedings of the National Academy of
  Sciences}} \textbf{118}, e2014564118 (2021).

\bibitem{allen2021indoor}
JG Allen, AM Ibrahim, {Indoor air changes and potential implications for
  SARS-CoV-2 transmission}.
\newblock {\em {Jama}} \textbf{325}, 2112--2113 (2021).

\bibitem{wang2021airborne}
CC Wang, et~al., Airborne transmission of respiratory viruses.
\newblock {\em {Science}} \textbf{373}, eabd9149 (2021).

\bibitem{lopman2021framework}
BA Lopman, et~al., {A framework for monitoring population immunity to
  SARS-CoV-2}.
\newblock {\em {Annals of Epidemiology}} \textbf{63},
  75--78 (2021).

\bibitem{fox2020impact}
SJ Fox, et~al., {The impact of asymptomatic COVID-19 infections on future
  pandemic waves}.
\newblock {\em {MedRxiv}} pp. 2020--06 (2020).

\bibitem{park2020reconciling}
SW Park, et~al., {Reconciling early-outbreak estimates of the basic
  reproductive number and its uncertainty: framework and applications to the
  novel coronavirus (SARS-CoV-2) outbreak}.
\newblock {\em {Journal of the Royal Society Interface}}
  \textbf{17}, 20200144 (2020).

\bibitem{smith1984assessment}
P Smith, L Rodrigues, P Fine, Assessment of the protective efficacy of vaccines
  against common diseases using case-control and cohort studies.
\newblock {\em {International journal of epidemiology}}
  \textbf{13}, 87--93 (1984).

\bibitem{buckner2021dynamic}
JH Buckner, G Chowell, MR Springborn, {Dynamic prioritization of COVID-19
  vaccines when social distancing is limited for essential workers}.
\newblock {\em {Proceedings of the National Academy of
  Sciences}} \textbf{118}, e2025786118 (2021).

\bibitem{bubar2021model}
KM Bubar, et~al., {Model-informed COVID-19 vaccine prioritization strategies by
  age and serostatus}.
\newblock {\em {Science}} \textbf{371}, 916--921 (2021).

\end{thebibliography}
